### 2018-04-17 README.Rmd
Readme Update

Or you can install this compendium as an R package, birthtiming, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("clanfear/birthtiming")
```
### Licenses

>>>>

Or you can install this compendium as an R package, birthtiming, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("clanfear/birthtiming")
```

### The R Package

This repository is organized as an R package. There are functions in this package, 
but they are only intended to be run within the `.Rmd` file that generates the article.

To generate the article from the `birthtiming` library, you may either:

1. Open and knit the `.Rmd` file found at `birthtiming/paper/paper.Rmd/` in your R libraries.
2. Clone this github repository and load the `.Rproj` file in RStudio, then knit the paper fron in `inst/paper/paper.Rmd`

In both cases, that directory will already contain a compiled version of the article current to the last commit to this repository.

### Licenses
